\tool: Revisiting BadUSB with Type-C

### 2021-03-21 WOOT/Files/experiment.tex
say goodbye

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% It is unfortunate that the user study is not part of the paper anymore.
\iffalse

To further validate our attacking scenario, we invited 10 volunteers, who are students in our university, to participate and conduct a user study.
Before the user study experiment, we disclosed to the volunteers how their data might be used and request permission from the volunteers and the university ethics review boards.
During the case study, volunteers took turns to use their phones for half an hour with \tool connected.
To obtain data close to real-life, they were requested to use phones just as they were normally using sharing power banks.
At the same time, we used scripts to perform \ac{OCR} recognition for each frame in the videos stream and stored all of the \ac{OCR} results in a database.

After each experiment, the raw video and the corresponding \ac{OCR} result file was generated automatically, then we presented these files to him/her, introduced our attack, told him/her to analyze the video file and replace certain characters of the private data that appear in the \ac{OCR} result file with asterisks. This protects their privacy and is also a mark for us to confirm that the data we found contains their private data. At last, he/she would destroy all original files, leave only the desensitized \ac{OCR} results for us.
%\shuqing{Do we need to mention that agreement the conference required here?}
%\hongyi{I'm also quite concern about this.}

\subsubsection{Result}

In total, there are 94,058 entries of data from 10 volunteers. An entry is a combination of the case number, the frame number and the desensitized \ac{OCR} result.
%\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim visited, especially the privacy data.
%\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
We searched the result database with the keywords \textit{account, username, password, phone number and email}, as well as the regular expression of email.
The records searched by such keywords and regular expressions are usually related to privacy information of users.
For example, when we searched with \textit{account} as a keyword, victim's accounts could be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example} and Table~\ref{table:information_extracted}.
%\shuqing{Statistics.}
At last, we found 4,172 of 94,058 records obtained by \tool which are related to privacy information, as shown in the Table~\ref{table:information_extracted}.

In summary, though we cannot directly obtain the user's password on the lock screen, we can still check all of the information presented on the screen, extract sensitive information including but not limited to social accounts, bank accounts, personal financial situation, etc., if the user unconsciously unlocks the screen.
It is worth mentioning that {secure keyboards} built in financial apps show their keyboard typing sequences, which can be easily captured by \tool.

\begin{table*}[t]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		\textbf{Keyword} & \textbf{Text}                                                             & \textbf{Name}                                   & \textbf{Frame Number} \\ \hline
		username                          & X 8B cas.******.edu.cn Username: 11****18 Password:                                        & \textless{}user1\textgreater{} & 385                                    \\ \hline
		username                          & Login Weibo Login with SMS and verification code ...... +86 151****4587                    & \textless{}user5\textgreater{} & 1947                                   \\ \hline
		username                          & QQ 14*****50| Login with phone number New user registration 2345678 9 0                    & \textless{}user3\textgreater{} & 4308                                   \\ \hline
		username                          & connect to *** username h*****l Save account information Open VPN.....                     & \textless{}user6\textgreater{} & 7925                                   \\ \hline
		phone number                      & Login with phone number ...... +86 186****2483 |                                           & \textless{}user1\textgreater{} & 313                                    \\ \hline
		phone number                      & Log in with your mobile phone number. ...... mobile phone number 131****9310 & \textless{}user9\textgreater{} & 210                                    \\ \hline
		@                                 & contact email 30*******7G@qq.com, contact phone 027-88******                               & \textless{}user7\textgreater{} & 5324                                   \\ \hline
		@                                 & Account 73*****5@qq.com @qq.com @163.com @gmail.com 	......      & \textless{}user6\textgreater{} & 621                                    \\ \hline
	\end{tabular}
	\linebreak
	\caption{Examples of Searching \ac{OCR} Results with Keywords.}
	\label{tab:ocr_keyword_example}
\end{table*}

\begin{table*}[t]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline
		\textbf{Keyword}                               & Account & Password & Phone number & Email & Username & Regexp for email~  \\
		\hline
		\textbf{Number of records containing keywords} & 680     & 1,596     & 1,510         & 164   & 522      & 78                 \\
		\hline
		\textbf{Total Number of Records} & \multicolumn{6}{c|}{4,172} \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Privacy Extraction Result.}
	\label{table:information_extracted}
\end{table*}

\fi

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% It is unfortunate that the user study is not part of the paper anymore.
